---
title: "Who does more pushups"
author: "Vanessa Michel"
date: "October 3, 2017"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?

In addition to who does more push ups, we will run a series of tests to show how significant of a difference there is between the 2 positions, if any. 

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The two variables involved are:

* **position**, which is a factor variable with two values ("LINE" and "SKILL");
* **pushups**, which is a numeric variable.

Although we do not believe that position determines how many pushups one can do, we may be able to prove that one position can do more than the other. 

Our variable analysis will show that we are interested in the relationship between two factor variables. Therefore, we will make box plots to examine the data graphically. 

We will also want to see if any relationship we find in the data between position and pushups might also be present in the population from which the data was gathered. To investigate this inferential question, we will use  fav stats and t  tests.





# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->



```{r echo=FALSE}
bwplot(pushups ~ position,
	data = pushups,
	panel = function(..., box.ratio) {
		panel.bwplot(..., fill = NULL, box.ratio = 0.1)
		panel.violin(..., col = "burlywood", border = "grey60", alpha = 0.5, varwidth = FALSE)})
```

Based on the box plot and violin plot we can see the two positions do not line up at all. This tells us that there is a significant difference between the two positions and number of pushups each can do. 

## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position, data=pushups)
```

Based on the fav stats test, we see that the average number of pushups players can do is significantly different between Line and Skill players. Average number of pushups for skill players is almost 3 times the average for line players. 



# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

We want to run a stats test of difference of means on weight between the skill and line players.

Our Null Hypothesis shall be:

$H_0$: There is no relationship between position and number of pushups a player can do in the selected population. 

The Alternative Hypothesis is:

$H_a$: There is a relationship between position and the number of pushups a player can do in the selected population. 


```{r}
ttestGC(pushups~position, data=pushups)

t.test(pushups~position, data=pushups)
```


The p-value tells us that we have a 95% confidence that there is a difference between position and the number of pushups players can do for our selected population. 


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->

Based on our findings, we see that skill players can do more pushups on average than line players. This was visually apparent when creating box and violin plots as the boxes did not cross paths at all. It was confirmed in the fav stats test, showing on average that skill players can do 3 times as many push ups as line players. Lastly, the t test just strengthened our results showing that there is a 95% confidence level of the difference between the 2 positions. There is enough data to conclude that not only is there a difference between the number of pushups skill players can do versus the number line players can do. We can also be very confident that skill players can do a significantly higher number of pushups than line players. 